GlobalSearchRegression.jl: \\ Building bridges between Machine Learning and Econometrics in Fat-Data scenarios

### 2019-07-12 paper/paper.tex
Update paper.tex
Add files via upload

% JuliaCon proceedings template
\documentclass{juliacon}
\setcounter{page}{1}

% Additional packages used%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{algorithm,amsmath,xcolor,caption}
%\usepackage[noend]{algpseudocode}
\usepackage{hyperref}
\DeclareMathOperator{\sgn}{sign}
\DeclareCaptionFont{lightblue}{\color{black}}
\captionsetup[algorithm]{labelfont={bf,lightblue}, textfont={it}}
%\renewcommand{\thealgorithm}{\arabic{algorithm}}
\usepackage{array}
\newcolumntype{C}[1]{>{\centering\arraybackslash}m{#1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\input{header}

\maketitle

\begin{abstract}
The aim of this paper is twofold. The first one is to describe a novel research-project aimed at building bridges between machine learning and econometric worlds. The second one is to introduce the main characteristics and comparative performance of the first Julia-native all-subset regression algorithm included in \verb GlobalSearchRegression.jl  (v1.0.3). As other available alternatives, this algorithm allows researchers to obtain the best model specification among all possible covariate combinations - in terms of user defined information criteria-, but up to 3165 and 197 times faster than STATA and R alternatives, respectively. 
\end{abstract}

\section{Introduction}
\label{sec:introduction}
While allowing for better and more accurate analysis (and forecasts), fat-data availability generates a revival of Bellman’s \cite{Bellman1961} -and newer- high-dimensionality concerns:
\begin{enumerate}
    \item Exponential increase in required information and execution time \cite{Yu2003} ;
    \item Overfitting risk \cite{Defernez1999}; 
    \item Less-informative euclidean distances \cite{Aggarwal2001}; and
    \item Unfeasible estimators \cite{Buhlmann2011}. 
\end{enumerate}

@@

\section{Package's main features}
\label{sec:packagefeatures}
%

@@

Through the gsreg function of the \verb interface.jl  internal package, users set the appropriate database to be used, the general unrestricted model -GUM, which defines the search space- and additional options for model selection. With this information and complementary supporting functions and definitions provided by \verb strings.jl  -i.e. error messages-, \verb utils.jl  -i.e. equation formatting, combinatorial analysis, database manipulation, sorting results, etc.- and \verb gsreg_results.jl  -i.e. the structure to save estimation results-, the \verb core.jl  package perform the all-subset-regression algorithm explained in the pseudocode below, to obtain the following outputs: 1) a matrix -optionally exported to a csv file through \verb utils.jl-  including regression coefficients, selection criteria, observations and (optionally) t-test, residual tests, averaging-weights and out-of-sample metrics for every alternative model; 2) a text file -also displayed on screen- which contains the best model specification and (optionally) model averaging results in terms of the user-selected information criteria -see multiple examples in \verb runtest.jl-. \vskip 6pt

%%%%%%%%%%%%%%%%%%%%%%% Algorithm 1
\begin{algorithm}[ht]
  \scriptsize
  \caption{module Core.jl}
  \begin{enumerate}

@@

\textbf{end} module \verb Core.jl .
\end{algorithm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Comparative performance against \textit{R} and \textit{STATA}}
\label{sec:comparativeperf}

%%%%%%%%%%%%%%%%%% Table 1
\begin{table*}[!t]
\tabcolsep1pt
\centering
\tbl{Average execution time and speed-up metrics -over 5 runs-}{
    \scalebox{0.8}{
    \begin{tabular}{|C{1cm}|C{1cm}|C{1cm}|C{1.5cm}|C{1.5cm}|C{1.5cm}|C{1.5cm}|C{1.5cm}|C{1.5cm}|C{1.5cm}|C{1.5cm}|}
    \hline
    \multirow{Cov.} & \multirow{Obs} & \multirow{Threads} & \multicolumn{3}{c|}{Execution time (in seconds)} & \multicolumn{3}{c|}{Parallel Speed-up} & \multicolumn{2}{c|}{Julia Speed-up} \\
\cline{4-11}      &   &   & Julia & R & Stata & Julia & R & Stata & Over R & Over Stata \\
    \hline
    15 & 100 & 1 & 14.0 & 69.1 & 646.6 & 1.0 & 1.0 & 1.0 & 4.9 & 46.2 \\
    \hline
    15 & 100 & 4 & 17.0 & 33.4 & 80.3 & 0.8 & 2.1 & 8.0 & 2.0 & 4.7 \\
    \hline
    15 & 100 & 16 & 22.0 & 23.6 & 22.1 & 0.6 & 2.9 & 29.2 & 1.1 & 1.0 \\
    \hline
    15 & 100 & 32 & 31.4 & 22.3 & 15.1 & 0.4 & 3.1 & 43.0 & 0.7 & 0.5 \\
    \hline
    15 & 1000 & 1 & 18.6 & 74.9 & 667.5 & 1.0 & 1.0 & 1.0 & 4.0 & 35.9 \\
    \hline
    15 & 1000 & 4 & 18.5 & 35.3 & 81.6 & 1.0 & 2.1 & 8.2 & 1.9 & 4.4 \\
    \hline
    15 & 1000 & 16 & 22.2 & 24.6 & 23.3 & 0.8 & 3.1 & 28.7 & 1.1 & 1.0 \\
    \hline
    15 & 1000 & 32 & 31.5 & 21.5 & 16.0 & 0.6 & 3.5 & 41.6 & 0.7 & 0.5 \\
    \hline
    15 & 10000 & 1 & 61.6 & 142.0 & 809.0 & 1.0 & 1.0 & 1.0 & 2.3 & 13.1 \\
    \hline
    15 & 10000 & 4 & 30.5 & 61.4 & 114.7 & 2.0 & 2.3 & 7.1 & 2.0 & 3.8 \\
    \hline
    15 & 10000 & 16 & 25.7 & 38.4 & 37.3 & 2.4 & 3.7 & 21.7 & 1.5 & 1.5 \\
    \hline
    15 & 10000 & 32 & 33.4 & 35.5 & 26.7 & 1.8 & 4.0 & 30.3 & 1.1 & 0.8 \\
    \hline
    20 & 100 & 1 & 169.2 & 10538.9 & 535693.2 & 1.0 & 1.0 & 1.0 & 62.3 & 3165.1 \\
    \hline
    20 & 100 & 4 & 65.6 & 9275.4 & 75510.2 & 2.6 & 1.1 & 7.1 & 141.4 & 1151.1 \\
    \hline
    20 & 100 & 16 & 44.7 & 8855.2 & 4526.3 & 3.8 & 1.2 & 118.4 & 197.9 & 101.2 \\
    \hline
    20 & 100 & 32 & 51.2 & 8732.4 & 1658.2 & 3.3 & 1.2 & 323.0 & 170.7 & 32.4 \\
    \hline
    20 & 1000 & 1 & 362.4 & 10765.9 &   & 1.0 & 1.0 &   & 29.7 &  \\
    \hline
    20 & 1000 & 4 & 119.0 & 9352.3 &   & 3.0 & 1.2 &   & 78.6 &  \\
    \hline
    20 & 1000 & 16 & 58.8 & 8926.4 &   & 6.2 & 1.2 &   & 151.8 &  \\
    \hline
    20 & 1000 & 32 & 59.8 & 8753.9 &   & 6.1 & 1.2 &   & 146.4 &  \\
    \hline
    20 & 10000 & 1 & 2338.4 & 13218.9 &   & 1.0 & 1.0 &   & 5.7 &  \\
    \hline
    20 & 10000 & 4 & 629.4 & 10287.9 &   & 3.7 & 1.3 &   & 16.3 &  \\
    \hline
    20 & 10000 & 16 & 198.6 & 9392.3 &   & 11.8 & 1.4 &   & 47.3 &  \\
    \hline
    20 & 10000 & 32 & 149.5 & 9041.6 &   & 15.6 & 1.5 &   & 60.5 &  \\
    \hline
    25 & 100 & 1 & 6700.7 &   &   & 1.0 &   &   &   &  \\
    \hline
    25 & 100 & 4 & 1937.7 &   &   & 3.5 &   &   &   &  \\
    \hline
    25 & 100 & 16 & 913.7 &   &   & 7.3 &   &   &   &  \\
    \hline
    25 & 100 & 32 & 803.9 &   &   & 8.3 &   &   &   &  \\
    \hline
    25 & 1000 & 1 & 14257.4 &   &   & 1.0 &   &   &   &  \\
    \hline
    25 & 1000 & 4 & 3954.2 &   &   & 3.6 &   &   &   &  \\
    \hline
    25 & 1000 & 16 & 1471.4 &   &   & 9.7 &   &   &   &  \\
    \hline
    25 & 1000 & 32 & 1159.9 &   &   & 12.3 &   &   &   &  \\
    \hline
    25 & 10000 & 1 & 93450.0 &   &   & 1.0 &   &   &   &  \\
    \hline
    25 & 10000 & 4 & 23783.8 &   &   & 3.9 &   &   &   &  \\
    \hline
    25 & 10000 & 16 & 6825.6 &   &   & 13.7 &   &   &   &  \\
    \hline
    25 & 10000 & 32 & 4660.4 &   &   & 20.1 &   &   &   &  \\
    \hline
    \end{tabular}    }   }
\end{table*}

@@

Despite some \verb GlobalSearchRegression.jl  specific features to be examined below, our all-subset-regression algorithm benefits from the well-known Julia language efficiency for High Performance Computing tasks. \vskip 6pt

%%%%%%%%%%%%%%%%%% Table 2
\begin{table}[!h]
\centering
\tbl{Julia speed-up over STATA and R in basic functions}{
    \begin{tabular}{|l|c|c|}
    \hline
    Function & Speed-up over R & Speed-up over Stata \\
    \hline
    \hline
    recursion\_fibonacci & 251.28 & 76.92 \\
    \hline
    recursion\_quicksort & 32.36 & 48.54 \\
    \hline
    matrix\_multiply & 11.6 & 14.07 \\
    \hline
    iteration\_pi\_sum & 14.33 & 26.89 \\
    \hline
    matrix\_statistics & 7.65 & 44.92 \\
    \hline
    parse\_integers & 28.4 & 49.38 \\
    \hline
    userfunc\_mandelbrot & 175.44 & 368.42 \\
    \hline
    \hline
    Simple-Average & 74.44 & 89.88 \\
    \hline
    Weighted-Average & 12.15 & 22.01 \\
    \hline
    \end{tabular}
    }
    \caption*{Note: Weighted-average were estimated as the Ratio between total execution time for R or Stata, and Julia's total execution time -for all basic functions-. Benchmarkings were obtained using a i7-4700MQ quad-core build, with 8 GiB of DDR3 1600 Mhz RAM, under Windows 8 and running Julia 1.1.0, Stata 15 and R 3.5.3}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\verb GlobalSearchRegression.jl  OLS estimation through QR-decompositions outperform existing Julia alternatives (like \verb GLM.jl)  allowing for large speed-ups compared with \verb R-lm    and \verb Stata-regress  commands. The following table shows execution time differences for a 200 covariates - 1000 observations - multivariate linear regression \footnote{Execution times were calculated for alternative OLS algorithms available for all-subset-regression packages in Julia, R and Stata.}:

%%%%%%%%%%%%%%%%%% Table 3
\begin{table}[htbp]
  \centering
\tbl{Execution times for different OLS algorithms in R, Stata and Julia}{
    \begin{tabular}{|c|c|c|c|c|}
    \hline
      & GlobalSearchRegression.jl &R-lm & Stata-reg & GLM.jl \\
    \hline
    Execution time & 0.012 & 0.06 & 0.2 & 0.023 \\
    \hline
    Speed-up & 1 & 5 & 16.67 & 1.92 \\
    \hline
    \end{tabular}}
    \caption*{Note: Execution times were obtained using a i7-7500 dual-core build, with 8 GiB of DDR4 RAM, under Windows 10 and running Julia 1.1.0, Stata 13 and RStudio 3.6.0. Speed-ups are obtaining dividing each execution time by the GlobalSearchRegression.jl execution time.}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%

It must be notice that execution times are compilation-free, because all-subset-regression algorithms must perform thousand to millions of regressions where compilation time is absent (it only affects the first regression).

\section{Conclusion}
\label{sec:con}

\begin{quote}
\textit{"There are a number of areas where there would be opportunities for fruitful collaboration between econometrics and machine learning [... and] the most important area for collaboration involves causal inference"}. \cite{varian2014}
\end{quote}

@@

\section{Acknowledgments}
\label{sec:ackno}
This research benefited from the financial support of 1) the National Scientific and Technical Research Council and the YPF-Foundation (PIO CONICET-YPF 13320150100020CO); and 2) the National Agency for Scientific and Technological Promotion (PICT-2017-0867). We would also like to thank PhD. Jorge Carrera for his technical assistance on Big-data econometric algorithms.
\input{bib.tex}

@@

>>>>

% JuliaCon proceedings template
\documentclass{juliacon}
\usepackage{amsmath}
\setcounter{page}{1}

\begin{document}
\input{header}
\maketitle
\begin{abstract}

The aim of this paper is twofold. The first one is to describe a novel research-project aimed at building bridges between machine learning and econometric worlds. The second one is to introduce the main characteristics and comparative performance of the first Julia-native all-subset regression algorithm included in \verb GlobalSearchRegression.jl  (v1.0.3). As other available alternatives, this algorithm allows researchers to obtain the best model specification among all possible covariate combinations - in terms of user defined information criteria-, but up to 3165 and 197 times faster than STATA and R alternatives, respectively.

\end{abstract}

\section{Introduction}
While allowing for better and more accurate analysis (and forecasts), fat-data availability generates a revival of Bellman’s \cite{Bellman1961} -and newer- high-dimensionality concerns:
\begin{enumerate}
    \item Exponential increase in required information and execution time \cite{Yu2003} ;
    \item Overfitting risk \cite{Defernez1999}; 
    \item Less-informative euclidean distances \cite{Aggarwal2001}; and
    \item Unfeasible estimators \cite{Buhlmann2011}. 
\end{enumerate}

@@

\section{Package's main features}
\label{sec:packagefeatures}

@@

Through the gsreg function of the \verb interface.jl  internal package, users set the appropriate database to be used, the general unrestricted model -GUM, which defines the search space- and additional options for model selection. With this information and complementary supporting functions and definitions provided by \verb strings.jl  -i.e. error messages-, \verb utils.jl  -i.e. equation formatting, combinatorial analysis, database manipulation, sorting results, etc.- and \verb gsreg_results.jl  -i.e. the structure to save estimation results-, the \verb core.jl  package perform the all-subset-regression algorithm explained in the pseudocode below, to obtain the following outputs: 1) a matrix -optionally exported to a csv file through \verb utils.jl-  including regression coefficients, selection criteria, observations and (optionally) t-test, residual tests, averaging-weights and out-of-sample metrics for every alternative model; 2) a text file -also displayed on screen- which contains the best model specification and (optionally) model averaging results in terms of the user-selected information criteria -see multiple examples in \verb runtest.jl-. \vskip 6pt
\break

%%%%%%%%%%%%%%%%%%%%%%% Algorithm 1
\begin{listing}
\hline
\center{ \textbf{Pseudo-code for module Core.jl}}
\vspace{2mm}
\hline
  \begin{enumerate}

@@

\begin{flushleft}
\textbf{end} module \verb Core.jl . \hfill
\end{flushleft}
\hline
\end{listing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Comparative performance against \textit{R} and \textit{STATA}}
\label{sec:comparativeperf}

%%%%%%%%%%%%%%%%%% Table 1
\begin{table*}[!t]
\centering
\tbl{Average execution time and speed-up metrics -over 5 runs-}{
\scalebox{0.85}{
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
    \hline
    \multirow{Cov.} & \multirow{Obs} & \multirow{Threads} & \multicolumn{3}{|c|}{Execution time (in seconds)} & \multicolumn{3}{
    c|}{Parallel Speed-up} & \multicolumn{2}{|c|}{Julia Speed-up} \\
\cline{4-11}      &   &   & Julia & R & Stata & Julia & R & Stata & Over R & Over Stata \\
    \hline
    15 & 100 & 1 & 14.0 & 69.1 & 646.6 & 1.0 & 1.0 & 1.0 & 4.9 & 46.2 \\
    \hline
    15 & 100 & 4 & 17.0 & 33.4 & 80.3 & 0.8 & 2.1 & 8.0 & 2.0 & 4.7 \\
    \hline
    15 & 100 & 16 & 22.0 & 23.6 & 22.1 & 0.6 & 2.9 & 29.2 & 1.1 & 1.0 \\
    \hline
    15 & 100 & 32 & 31.4 & 22.3 & 15.1 & 0.4 & 3.1 & 43.0 & 0.7 & 0.5 \\
    \hline
    15 & 1000 & 1 & 18.6 & 74.9 & 667.5 & 1.0 & 1.0 & 1.0 & 4.0 & 35.9 \\
    \hline
    15 & 1000 & 4 & 18.5 & 35.3 & 81.6 & 1.0 & 2.1 & 8.2 & 1.9 & 4.4 \\
    \hline
    15 & 1000 & 16 & 22.2 & 24.6 & 23.3 & 0.8 & 3.1 & 28.7 & 1.1 & 1.0 \\
    \hline
    15 & 1000 & 32 & 31.5 & 21.5 & 16.0 & 0.6 & 3.5 & 41.6 & 0.7 & 0.5 \\
    \hline
    15 & 10000 & 1 & 61.6 & 142.0 & 809.0 & 1.0 & 1.0 & 1.0 & 2.3 & 13.1 \\
    \hline
    15 & 10000 & 4 & 30.5 & 61.4 & 114.7 & 2.0 & 2.3 & 7.1 & 2.0 & 3.8 \\
    \hline
    15 & 10000 & 16 & 25.7 & 38.4 & 37.3 & 2.4 & 3.7 & 21.7 & 1.5 & 1.5 \\
    \hline
    15 & 10000 & 32 & 33.4 & 35.5 & 26.7 & 1.8 & 4.0 & 30.3 & 1.1 & 0.8 \\
    \hline
    20 & 100 & 1 & 169.2 & 10538.9 & 535693.2 & 1.0 & 1.0 & 1.0 & 62.3 & 3165.1 \\
    \hline
    20 & 100 & 4 & 65.6 & 9275.4 & 75510.2 & 2.6 & 1.1 & 7.1 & 141.4 & 1151.1 \\
    \hline
    20 & 100 & 16 & 44.7 & 8855.2 & 4526.3 & 3.8 & 1.2 & 118.4 & 197.9 & 101.2 \\
    \hline
    20 & 100 & 32 & 51.2 & 8732.4 & 1658.2 & 3.3 & 1.2 & 323.0 & 170.7 & 32.4 \\
    \hline
    20 & 1000 & 1 & 362.4 & 10765.9 &   & 1.0 & 1.0 &   & 29.7 &  \\
    \hline
    20 & 1000 & 4 & 119.0 & 9352.3 &   & 3.0 & 1.2 &   & 78.6 &  \\
    \hline
    20 & 1000 & 16 & 58.8 & 8926.4 &   & 6.2 & 1.2 &   & 151.8 &  \\
    \hline
    20 & 1000 & 32 & 59.8 & 8753.9 &   & 6.1 & 1.2 &   & 146.4 &  \\
    \hline
    20 & 10000 & 1 & 2338.4 & 13218.9 &   & 1.0 & 1.0 &   & 5.7 &  \\
    \hline
    20 & 10000 & 4 & 629.4 & 10287.9 &   & 3.7 & 1.3 &   & 16.3 &  \\
    \hline
    20 & 10000 & 16 & 198.6 & 9392.3 &   & 11.8 & 1.4 &   & 47.3 &  \\
    \hline
    20 & 10000 & 32 & 149.5 & 9041.6 &   & 15.6 & 1.5 &   & 60.5 &  \\
    \hline
    25 & 100 & 1 & 6700.7 &   &   & 1.0 &   &   &   &  \\
    \hline
    25 & 100 & 4 & 1937.7 &   &   & 3.5 &   &   &   &  \\
    \hline
    25 & 100 & 16 & 913.7 &   &   & 7.3 &   &   &   &  \\
    \hline
    25 & 100 & 32 & 803.9 &   &   & 8.3 &   &   &   &  \\
    \hline
    25 & 1000 & 1 & 14257.4 &   &   & 1.0 &   &   &   &  \\
    \hline
    25 & 1000 & 4 & 3954.2 &   &   & 3.6 &   &   &   &  \\
    \hline
    25 & 1000 & 16 & 1471.4 &   &   & 9.7 &   &   &   &  \\
    \hline
    25 & 1000 & 32 & 1159.9 &   &   & 12.3 &   &   &   &  \\
    \hline
    25 & 10000 & 1 & 93450.0 &   &   & 1.0 &   &   &   &  \\
    \hline
    25 & 10000 & 4 & 23783.8 &   &   & 3.9 &   &   &   &  \\
    \hline
    25 & 10000 & 16 & 6825.6 &   &   & 13.7 &   &   &   &  \\
    \hline
    25 & 10000 & 32 & 4660.4 &   &   & 20.1 &   &   &   &  \\
    \hline 
    \end{tabular}}}
\end{table*}

@@

Despite some \verb GlobalSearchRegression.jl  specific features to be examined below, our all-subset-regression algorithm benefits from the well-known Julia language efficiency for High Performance Computing tasks.

\vspace{-2mm}

%%%%%%%%%%%%%%%%%% Table 2
\begin{table}[!h]
\centering
\tbl{Julia speed-up over STATA and R in basic functions}{
    \begin{tabular}{|l|c|c|}
    \hline
    Function & Speed-up over R & Speed-up over Stata \\
    \hline
    \hline
    recursion\_fibonacci & 251.28 & 76.92 \\
    \hline
    recursion\_quicksort & 32.36 & 48.54 \\
    \hline
    matrix\_multiply & 11.6 & 14.07 \\
    \hline
    iteration\_pi\_sum & 14.33 & 26.89 \\
    \hline
    matrix\_statistics & 7.65 & 44.92 \\
    \hline
    parse\_integers & 28.4 & 49.38 \\
    \hline
    userfunc\_mandelbrot & 175.44 & 368.42 \\
    \hline
    \hline
    Simple-Average & 74.44 & 89.88 \\
    \hline
    Weighted-Average & 12.15 & 22.01 \\
    \hline
    \multicolumn{3}{p{8.5cm}}{Note: Weighted-average were estimated as the Ratio between total execution time for R or Stata, and Julia's total execution time. Benchmarkings were obtained using a i7-4700MQ quad-core build, with 8 GiB of DDR3 1600 Mhz RAM, under Windows 8 and running Julia 1.1.0, Stata 15 and R 3.5.3}
    \end{tabular}
    }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\break

@@

\verb GlobalSearchRegression.jl  OLS estimation through QR-decompositions outperform existing Julia alternatives (like \verb GLM.jl)  allowing for large speed-ups compared with \verb R-lm    and \verb Stata-regress  commands. Table 3 shows execution time differences for a 200 covariates - 1000 observations - multivariate linear regression \footnote{Execution times were calculated for alternative OLS algorithms available for all-subset-regression packages in Julia, R and Stata.}.
\vskip 6pt

It must be notice that execution times are compilation-free, because all-subset-regression algorithms must perform thousand to millions of regressions where compilation time is absent (it only affects the first regression).
\vskip 6pt

\break
%%%%%%%%%%%%%%%%%% Table 3
\begin{table}[!h]
  \centering
\tbl{Execution times for OLS algorithms in R, Stata and Julia}{
    \begin{tabular}{|c|c|c|c|c|}
    \hline
      & GlobalSearchRegression.jl &R-lm & Stata-reg & GLM.jl \\
    \hline
    Exec. time & 0.012 & 0.06 & 0.2 & 0.023 \\
    \hline
    Speed-up & 1 & 5 & 16.67 & 1.92 \\
    \hline
    \multicolumn{5}{p{8.5cm}}{Note: Execution times were obtained using a i7-7500 dual-core build, with 8 GiB of DDR4 RAM, under Windows 10 and running Julia 1.1.0, Stata 13 and RStudio 3.6.0. Speed-ups are obtaining dividing each execution time by the GlobalSearchRegression.jl execution time.} \\
    \end{tabular}}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion}
\label{sec:con}
\vspace{2mm}
\begin{quote}
\textit{"There are a number of areas where there would be opportunities for fruitful collaboration between econometrics and machine learning [... and] the most important area for collaboration involves causal inference"}. \cite{varian2014}
\end{quote}
\vspace{2mm}

@@

\section{Acknowledgments}
\label{sec:ackno}
This research benefited from the financial support of 1) the National Scientific and Technical Research Council and the YPF-Foundation (PIO CONICET-YPF 13320150100020CO); and 2) the National Agency for Scientific and Technological Promotion (PICT-2017-0867). We would also like to thank PhD. Jorge Carrera for his technical assistance on Big-data econometric algorithms.

\input{bib.tex}

@@

% Inspired by the International Journal of Computer Applications template
